---
title: "Map on a Website"
author: "Carl"
date: "10/28/2020"
output: html_document
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, results = "hide",
                      cache = TRUE)

# install.packages(c("tmap", "raster", "sf"))
library(tmap)      #interactive maps, raster + vector layers
library(raster)       #Main raster library
library(tidyverse)    #our old friend
library(sf)           #to work with simple features data
```  



```{r}
tmp <- tempfile()
download.file("https://dsl.richmond.edu/panorama/redlining/static/fullshpfile.zip", tmp)
unzip(tmp)

tmp <- tempfile()
download.file("https://data.ca.gov/dataset/e212e397-1277-4df3-8c22-40721b095f33/resource/b0007416-a325-4777-9295-368ea6b710e6/download/ca-county-boundaries.zip", tmp) 
unzip(tmp)
```


```{r}
holc <- st_read("fullshpfile/shapefile")
ndvi_birmingham <- raster("../geospatial-chapman-boettiger/data/NDVI/composite_birmingham.tif")

shp_birmingham <- holc %>% filter(city == "Birmingham") %>% select(holc_grade, geometry)
```


# Birmingham Redlining

In August 2020, [Christopher Schell](http://directory.tacoma.uw.edu/employee/cjschell) and collegues published a review in *Science* on ['The ecological and evolutionary consequences of systemic racism in urban environments'](https://science.sciencemag.org/content/early/2020/08/12/science.aay4497) (DOI: 10.1126/science.aay4497), showing how systematic racism and classism  has significant impacts on ecologial and evolutionary processes within urban environments. Here we explore a subset of the data used to support these findings in this review and the broaded literature.


```{r results="markup", cache = FALSE}
tmap_mode("view")
tm_shape(shp_birmingham) + 
    tm_polygons("holc_grade", alpha = 0.3)  + 
    tm_shape(ndvi_birmingham) +
    tm_raster(alpha=0.3)
```


# Another Heading

- list
- items
